Stabilization-Free Virtual Element Methods

### 2023-08-13 ex_shared.tex
remove \XH

% Title. If the supplement option is on, then "Supplementary Material"
% is automatically inserted before the title.
\title{Virtual Element Methods Without Extrinsic Stabilization\thanks{\today
\funding{%The second author is the corresponding author. 
The second author was supported by the National Natural Science Foundation of
China {\color{red} (NSFC) (Grant No. 12171300)}, and the Natural Science Foundation of Shanghai
{\color{red}(Grant No. 21ZR1480500)}. The first and third authors were supported by the National Natural
Science Foundation of China (NSFC) (Grant No. 12261131501, 11871413), and the construction of innovative provinces in Hunan Province (Grant No. 2021GK1010)}}}

>>>>

% Title. If the supplement option is on, then "Supplementary Material"
% is automatically inserted before the title.
\title{Virtual Element Methods Without Extrinsic Stabilization\thanks{\today
\funding{%The second author is the corresponding author. 
The second author was supported by the National Natural Science Foundation of
China (NSFC) (Grant No. 12171300), and the Natural Science Foundation of Shanghai
(Grant No. 21ZR1480500). The first and third authors were supported by the National Natural
Science Foundation of China (NSFC) (Grant No. 12261131501, 11871413), and the construction of innovative provinces in Hunan Province (Grant No. 2021GK1010)}}}
